Phase paper outline

### 2014-05-15 Manuscript/Phase_detectors_outline.tex
started methods

@@

\subsection*{Simulation}
\begin{itemize}
\item Generation of data
	\begin{itemize}
	\item A sinusoidal signal containing (number?) frequencies were generated to resemble a typical arterial pressure recording. 
	\item A second sinusoidal signal was generated so that it was the same as the original signal except each frequency was time-varying within a narrow range.
	\item Noise was added to the signal at increasing levels so SNR ranged from $1-100 dB$
	\item Each frequency was isolated with a bandpass filter (elliptic?)
	\end{itemize}
\item Testing the phase detectors
	\begin{itemize}
	\item Each phase detector was used to determine the instantaneous phase of each frequency band isolated from the simulated data
	\end{itemize}

\subsection*{Physiological data}
\begin{itemize}
\item 
\end{itemize}

>>>>

\subsection*{Potential physiology journals}

\begin{itemize}
\item Acta physiologica
\item Physiological Reports
\item AJP Heart/regulatory - Innovative methodology
\item The Journal of Physiology - techniques for physiology \textit{I think this kind of thing might be best}
\item The Journal of General Physiology - methods and approaches
\item Physiological measurement
\item Journal of experimental physiology
\end{itemize}

\subsection*{Potential engineering journals}
\begin{itemize}
\item IEEE transactions on biomedical engineering
\item IEEE transactions on signal processing
\item IEEE signal processing letters
\item Signal processing and control
\item Signal processing
\item Annals of biomedical engineering
\end{itemize}

@@

\subsection*{Simulation}
\begin{itemize}
\item Generation of data
	\begin{itemize}
	\item A sinusoidal signal containing (number?) frequencies were generated to resemble a typical arterial pressure recording. 
	\item A second sinusoidal signal was generated so that it was the same as the original signal except each frequency was time-varying within a narrow range.
	\item Noise was added to the signal at increasing levels so SNR ranged from $1-100 dB$
	\item Each frequency was isolated with a bandpass filter (elliptic?)
	\end{itemize}
\item Testing the phase detectors
	\begin{itemize}
	\item Each phase detector was used to determine the instantaneous phase of each frequency band isolated from the simulated data
	\item The accuracy of the estimated instantaneous phase was calculated as ???
	\end{itemize}

\subsection*{Accuracy of phase estimates}
Accuracy $A$ is the mean difference between the estimated phase of a signal and its true phase. 
$$ A = \frac{1}{N} \sum_{m=1}^{N} \frac{\left| \phi _{true} (t) - \phi _{est} (t) \right|}{\phi _{true} (t)} $$

\subsection*{Physiological data}
\begin{itemize}
\item Renal cortical perfusion
	\begin{itemize}
	\item phase synchronization among regions of the kidney
	\end{itemize}
\item BP and Heart rate
	\begin{itemize}
	\item phase lag between changes in heart rate and changes in BP
	\end{itemize}
\item Something about SCG or ECG
\item cerebral blood flow
\end{itemize}
